---
title: "MATH 216 Homework 2 Shiny App"
author: "Shannia Fu"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(babynames)
library(ggplot2movies)
```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

## Question 2:

In the file `HW-2_Shiny_App.Rmd`, build the Shiny App discussed in Lec09 on
Monday 10/3: Using the `movies` data set in the `ggplot2movies` data set, make a
Shiny app that

* Plots budget on the x-axis and rating on the y-axis
* Instead of having a radio button to select the genre of movie (`Action`,
`Animation`, `Comedy`, etc), have a radio button that allows you to toggle
between comedies and non-comedies. This app should be simpler.

```{r eruptions, echo=FALSE}
comedy_movies <- movies %>% 
  mutate(is_comedy=(ifelse(Comedy==1, "Comedy", "Not Comedy")))
inputPanel(
  # Input comedy/not comedy
  radioButtons("Comedy", label = "Is it a comedy?", choices=c("Comedy", "Not Comedy"), selected="Comedy", inline=FALSE)
)

renderPlot({
  
  # Generate Plots
  more_comedy <- comedy_movies %>% 
    filter(!is.na(budget) & !is.na(rating)) %>% 
    filter(is_comedy==input$Comedy)
  ggplot(data=more_comedy, aes(x=budget, y=rating)) + 
    geom_point() + 
    scale_x_log10()
  
})
```
